Word Sense Disambiguation

### 2011-04-12 paper/paper.Rnw
talked about the parser

\documentclass{article}
\title{Word Sense Disambiguation}
\author{
Alec Story
Ansu Abraham
Craig Frey
Dustin Tiedemann
Michael Zhu
Thomas Levine
Whitney Foster
}

@@

>>>>

\documentclass{article}
\usepackage{url}
\title{Word Sense Disambiguation}
\author{
Alec Story
Ansu Abraham
Craig Frey\\
Dustin Tiedemann
Michael Zhu
Thomas Levine
Whitney Foster\\
}

@@

\section{Dependency Parsing}

We included as one feature the MaltParser dependency parser, and used the
engmalt.linear.mco linear support vector machine
configuration\footnote{\url{http://maltparser.org/mco/english_parser/engmalt.html}}
for parsing (the other option was a an SVM with a polynomial kernel, which the
Malt website said would just as accurately, more slowly, but with less memory,
so we decided to go with the faster option).
